---
title: "Stock Reporting - `r params$stock`"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
params:
  stock: "GOOG"
---

```{r setup, include=FALSE}
source("processing.r");
datazoo <- get.hist.quote(paste(params$stock), quiet=FALSE)
data <- as.data.frame(datazoo)
data$date <- as.Date(time(datazoo))
```
# All Time
Column {data-width=550}
-----------------------------------------------------------------------
### All Time Closing
```{r, echo=FALSE}
timePlot(data, data$date, data$Close)
```

### Daily maximum variance

```{r echo=FALSE}
timePlot(data, data$date, data$High - data$Low)
```

### Quarterly Closing

```{r echo=FALSE}
quarterPlot(datazoo)
```

Column {data-width=400}
-----------------------------------------------------------------------


### Daily Close vs Open

```{r echo=FALSE}
timePlot(data, data$date, data$Close - data$Open)
```


### Boxplot Closing - High Vs Low - Open Vs Close

```{r, echo=FALSE, message=FALSE}
tripleBoxPlot(data)
```

Column {data-width=50}
-----------------------------------------------------------------------

### Maximum Price

```{r}
max <- max(data$High)
valueBox(max, color = "primary")
```

### Maximum Gain in a day

```{r}
maxG <- max(data$Close - data$Open)
valueBox(maxG, color = "primary")
```

### Minimum Price

```{r}
min <- min(data$Low)
valueBox(min, color = "primary")
```

### Maximum Loss in a day

```{r}
minG <- min(data$Close - data$Open)
valueBox(minG, color = "primary")
```

### Standard Deviation

```{r}
stddev <- sd(data$Close)
valueBox(stddev, color = "primary")
```

### Mean

```{r}
mean <- mean(data$Close)
valueBox(mean, color = "primary")
```



# Last Year

Column {data-width=550}
-----------------------------------------------------------------------

### All Time Closing
```{r, echo=FALSE}
dataTail <- tail(data, 365)
timePlot(dataTail, dataTail$date, dataTail$Close)
```

### Daily maximum variance

```{r echo=FALSE}
timePlot(dataTail, dataTail$date, dataTail$High - dataTail$Low)
```

### Quarterly Closing

```{r echo=FALSE}
quarterPlot(tail(datazoo, 365))
```

Column {data-width=400}
-----------------------------------------------------------------------


### Daily Close vs Open

```{r echo=FALSE}
timePlot(dataTail, dataTail$date, dataTail$Close - dataTail$Open)
```


### Boxplot Closing - High Vs Low - Open Vs Close

```{r, echo=FALSE, message=FALSE}
tripleBoxPlot(dataTail)
```

Column {data-width=50}
-----------------------------------------------------------------------

### Maximum Price

```{r}
max_ly <- max(dataTail$High)
valueBox(max_ly, color = ifelse(max_ly > max, "success", "primary"))
```

### Maximum Gain in a day

```{r}
maxG_ly <- max(dataTail$Close - dataTail$Open)
valueBox(maxG_ly, color = "primary")
```

### Minimum Price

```{r}
min_ly <- min(dataTail$Low)
valueBox(min_ly, color = ifelse(min_ly > min, "success", "primary"))
```

### Maximum Loss in a day

```{r}
minG_ly <- min(dataTail$Close - dataTail$Open)
valueBox(minG_ly, color = ifelse(minG_ly > minG, "primary", "danger"))
```

### Standard Deviation

```{r}
stddev_ly <- sd(dataTail$Close)
valueBox(stddev_ly, color = "primary")
```

### Mean

```{r}
mean_ly <- mean(dataTail$Close)
valueBox(mean_ly, color = ifelse(mean_ly > mean, "success", "primary"))
```

# "Prophet" Forecasting

Column {data-width=550}
-----------------------------------------------------------------------

### Forecast from all data

```{r, echo=FALSE, warnings=FALSE}
forecastForecast(data$date, data$Close)
```

### Forecast from last years data

```{r, echo=FALSE, warnings=FALSE}
forecastForecast(dataTail$date, dataTail$Close)
```